Homicide Increases in the COVID-19 Era

### 2025-03-01 Draft2.qmd
Update Draft2.qmd

ggplot(crime_by_area, aes(y = numberOfCrimes, group = Bureau, x = Bureau)) + 
        geom_boxplot(aes(fill = Bureau))
```
###Interpretation

@@

>>>>

ggplot(crime_by_area, aes(y = numberOfCrimes, group = Bureau, x = Bureau)) + 
        geom_boxplot(aes(fill = Bureau))
```
## Interpretation

@@

## Interpretation
Homicide rates were low pre-pandemic and had a sharp increase since pandemic due to a reduction in income. Homicide rate reduces again after pandemic likely due to the economic recovery and increasing wages.
